---
title: "Manual Analysis of Stars"
output: html_notebook
---

We assume that you have already executed `dataset.Rmd` in RStudio and your environments are populated. 

## Stars outliers

Let's see what are the lowest ranking projects in the categories:

```{r}
get_lowest = function(dataset, columns) {
  dataset = dataset %>% select(id, url, stars, locs, snapshots, lifetime, commits, max_hindex1, users)
  result = dataset %>% arrange(locs) %>% head(20)
  dataset = dataset %>% filter(! id %in% result$id)
  result = rbind(result, dataset %>% arrange(snapshots) %>% head(20))
  dataset = dataset %>% filter(! id %in% result$id)
  result = rbind(result, dataset %>% arrange(lifetime) %>% head(20))
  dataset = dataset %>% filter(! id %in% result$id)
  result = rbind(result, dataset %>% arrange(commits) %>% head(20))
  dataset = dataset %>% filter(! id %in% result$id)
  result = rbind(result, dataset %>% arrange(max_hindex1) %>% head(20))
  result %>% mutate(url = paste0("<a href=\"", url, "\">", url, "</a>"))
}


datatable(get_lowest(java_stars, columns), escape = F)
```
DEP, DOC, DOC, TUT, BABY, UI, BABY, UI, UI, TUT
TUT, BABY, UI, UI, UI, UI, UI, UI, UI, BABY
UI, TUT, UI, UI, UI, BABY, BABY, UI, UI, UI
TUT, BABY, UI, UI, UI, UI, BABY, UI, UI, UI
EXT, FP, TUT, BABY, UI, EXT, UI, EXT, UI, BABY
EXT, TUT, BABY, FP, UI, TUT, FP, UI, FP, FP
EXT, EXT, EXT, TUT, TUT, TUT, UI, UI, UI, BABY
UI, UI, EXT, TUT, TUT, BABY, TUT, TUT, TUT, UI
DOC, UI, FP, BABY, EXT, UI, UI, FP, UI, UI
UI, TUT, FP, FP, UI, FP, BABY, UI, BABY, DOC 



```{r}
datatable(get_lowest(python_stars, columns), escape = F)
```
DOC,  DEP,  DEP,  BABY, DEP,  DOC,  TUT,  FP,   DEP,  BABY
DOC,  BABY, BABY, TUT,  FP,   DOC,  BABY, BABY, BABY, DOC
RES,  BABY, TUT,  FP,   BABY, DOC,  EXT,  BABY, DOC,  BABY
BABY, RES,  RES,  BABY, BABY, TUT,  DOC,  BABY, DOC,  BABY
EXT,  DOC,  BABY, EXT,  BABY, TUT,  BABY, BABY, BABY, BABY
RES,  RES,  RES,  FP,   RES,  BABY, BABY, BABY, DEP,  RES
RES,  BABY, RES,  RES,  RES,  BABY, RES,  RES,  FP,   EXT
TUT,  TUT,  RES,  EXT,  BABY, RES,  TUT,  BABY, BABY, DOC
DOC,  FP,   DOC,  FP,   RES,  DOC,  BABY, RES,  TUT,  FP 
FP,   FP,   RES,  DOC,  FP,   BABY, RES,  FP,   FP,   RES


```{r}
datatable(get_lowest(js_stars, columns), escape = F)
```
DEP, BABY, FP,   DOC,  BABY, DOC,  BABY, DOC,  TUT,  BABY
FP,  BABY, BABY, BABY, BABY, BABY, FP,   BABY, TUT,  EXT
TUT, BABY, TUT,  BABY, DOC,  TUT,  EXT,  TUT,  UI,   TUT
UI   UI,   UI,   DEP,  BABY, BABY, BABY, BABY, BABY, UI
FP   BABY  BABY  TUT   EXT   EXT   BABY  UI    BABY  TUT
BABY TUT   BABY  TUT   EXT   EXT   BABY  BABY  DEP   TUT
UI   TUT   TUT   BABY  TUT   BABY  EXT   TUT   TUT   BABY
DOC  BABY  UI    TUT   BABY  BABY  UI    TUT   UI    BABY
FP   BABY  UI    BABY  DOC   DOC   BABY  BABY  UI    FP
FP   FP    TUT   TUT   FP    UI    UI    TUT   BABY  BABY


Kind  Java Python JS
FP    10   13     9
EXT   9    5      7
UI    43   0      14
DOC   4    15     7
TUT   17   9      22
BABY  16   32     38
RES   0    21     0
DEP   1    5      3



## Manual Analysis of uninteresting stars

Let's see what is there in the uninteresting stars, language by language. We classify into the following categories:

False Positives = these are ok projects that for some error in the pipeline appear to have skewed statistics
External Projects = projects that are real, but whose development happens elsewhere (dumps of private company repos, etc.)
UI Widgets = UI widgets, such as Anrdoid, Browser, etc. not much of code or development, but real projects
Documentation = Mostly text, snippets repositories, etc. 
Tutorials = Sample projects, apps, etc. 
Baby projects = small projects that have little code and little development and don't fit other categories
Research Artifacts = Artifacts & demonstrations for papers, usually dumps of code
Deprecated = Deprecated projects with files removed (can still be found in history or other branch)
Errors = Not really in the language described

```{r}
datatable(java_stars %>% filter(id %in% java_uninteresting$id) %>% select(id, url, stars, max_hindex1, max_user_lifetime, lifetime, users, locs, snapshots, paths, commits) %>% mutate(url = paste0("<a href=\"", url, "\">", url, "</a>")), escape = F)
```

1  DOC  963877	https://github.com/twowaits/sde-interview-questions.git               Interview questions
2  DOC  952697	https://github.com/doocs/source-code-hunter.git                       Documentation
3  UI   47322	https://github.com/pomepuyn/blureffectforandroiddesign.git            Android Widget
4  EXT  38116	https://github.com/white-cat/thinkandroid.git                         Android Development Framework Dump
5  UI   114226	https://github.com/romainpiel/titanic.git                             Android Widget
6  BABY 749766	https://github.com/videlalvaro/gifsockets.git                         Funny small tiny app
7  UI   104161	https://github.com/markushi/android-circlebutton.git                  Android Widget
8  TUT  90635	https://github.com/romainguy/road-trip.git                            Android example app
9  UI   94982	https://github.com/flavienlaurent/discrollview.git                    Android Widget
10 TUT  185032	https://github.com/antoniolg/materialeverywhere.git                   Android example app    
11 EXT  3184	  https://github.com/xamarin/xobotos.git                                Android ported to C#
12 UI   60551	https://github.com/romannurik/android-monthcalendarwidget.git         Android Widget   
13 EXT  16722	https://github.com/designativedave/androrat.git                       Android Remote Management, Dump
14 DEP  735931	https://github.com/purplecabbage/phonegap-plugins.git                 Deprecated repo with plugins (code deleted, just readme & history)
15 UI   199219	https://github.com/chenupt/bezierdemo.git                             Andoid Widget  
16 EXT  13692	https://github.com/sonyxperiadev/apkanalyser.git                      Android APK analyzer, dump   
17 UI   131721	https://github.com/singwhatiwanna/pinnedheaderexpandablelistview.git  Android Widget
18 BABY 574496	https://github.com/rom1v/sndcpy.git                                   Android as microphone, maybe dump? 
19 UI   195347	https://github.com/bluemor/android-pulllayout.git                     Android App
20 EXT  459880	https://github.com/bytedance/boostmultidex.git                        Android Tool, Dump

```{r}
datatable(python_stars %>% filter(id %in% python_uninteresting$id) %>% select(id, url, stars, max_hindex1, max_user_lifetime, lifetime, users, locs, snapshots, paths, commits) %>% mutate(url = paste0("<a href=\"", url, "\">", url, "</a>")), escape = F)
```
1 	DOC  1112888	https://github.com/30-seconds/30-seconds-of-python.git              Short code snippets library   
2 	BABY 1061735	https://github.com/not-kennethreitz/osx-gcc-installer.git           GCC installer for OSX (not much python code, or code in general)
3 	DEP  1073048	https://github.com/p0cl4bs/wifi-pumpkin-deprecated.git              Deprecated, deleted, only in history
4 	DEP  1114344	https://github.com/automagica/automagica.git                        Deprecated (bought by a company), deleted, only in history
5 	RES  56779	  https://github.com/princeton-vl/cornernet.git                       Dump (seems from a paper's artifact)
6 	DOC  1166965	https://github.com/juliangaal/python-cheat-sheet.git                Documentation & snippets
7 	BABY 22175	  https://github.com/angusshire/greenhat.git                          Dump, or toy project - creates GH history:) Been there, seen that   
8 	DOC  25049	  https://github.com/fossasia/knitpat.git                             Knitting pattern - pretty much empty, have *no* idea what it is for and why it got so many stars
9 	EXT  88312	  https://github.com/nobody132/masr.git                               Speech Recogniotion for mandarin, dump
10	RES  51108	  https://github.com/arnaucube/coffeeminer.git                        Some mining, research, dump
11	RES  79484	  https://github.com/megvii-nanjing/ml-gcn.git                        ML Paper artifact, Dump
12	RES  55849	  https://github.com/brain-research/self-attention-gan.git            ML Paper artifact, Dump
13	DEP  1104116	https://github.com/mmmxcc/ss-panel-and-ss-py-mu.git                 Some chinese thing, not sure what it does, default branch empty, history & other branch
14	BABY 74664	  https://github.com/uvipen/quickdraw.git                             Toy drawing app (recognized from webcam) implementation, dump? 
15	DOC  1129478	https://github.com/alantur1ng/nlp-bert--chineseversion.git          Chinese translation for a NLP repo, docs? 
16	FP   1092223	https://github.com/jarun/imgp.git                                   Actual app, files w/o extension, so a proper project
17	TUT  101730	https://github.com/aladdinpersson/machine-learning-collection.git   ML Tutorials
18	DOC  1116939	https://github.com/lovelyyoshino/shadowsocks-hosts-or-v2ray.git     Collection of IP addresses I guess to bypass China's firewall?, few lines of python
19	DEP  1086202	https://github.com/docker-archive/dockercloud-haproxy.git           Deprecated, main branch empty, otherwise valid
20	EXT  92763	  https://github.com/ttcqaq/city-vein.git                             Urban networks visualizer, dead, drop
21	FP   1099940	https://github.com/mhsabbagh/green-recorder.git                     Audio recorder, valid (no extension)
22	RES  73766	  https://github.com/xiaomi-automl/falsr.git                          ML paper artifact, dump
23	EXT  44837	  https://github.com/openmihome/mihome-binary-protocol.git            Smart Home API, dump
24	DOC  1078062	https://github.com/chyyuu/ucore_os_docs.git                         Documentation in chinese
25	FP   1069121	https://github.com/heroku-python/pip-pop.git                        Valid, no extension
26	BABY 1066603	https://github.com/vpnguy-zz/ntpdos.git                             Vulnerability Script, valid
27	TUT  40913	  https://github.com/rnevius/minimal-django.git                       Example app
28	BABY 88417	  https://github.com/harshibar/common-intern.git                      Script that applies to hundreds of jobs, valid I guess
29	BABY 1128592	https://github.com/blacknbunny/cve-2018-10933.git                   Vulnerability, valid- ish
30	BABY 92768	  https://github.com/ssize-t/inlinec.git                              PLugin for inlining C in python, valid
31	EXT  15330	  https://github.com/hpdang/pdfinator.git                             Turns images to pdf, dump
32	EXT  22530	  https://github.com/ycjuan/kaggle-avazu.git                          Kaggle project dump
33	EXT  82736	  https://github.com/notadamking/stock-trading-environment.git        ML dump
34	BABY 1111529	https://github.com/mthbernardes/rsg.git                             Reverse shell, valid
35	EXT  41559	  https://github.com/keon/deepstock.git                               ML dump

```{r}
datatable(js_stars %>% filter(id %in% js_uninteresting$id) %>% select(id, url, stars, max_hindex1, max_user_lifetime, lifetime, users, locs, snapshots, paths, commits) %>% mutate(url = paste0("<a href=\"", url, "\">", url, "</a>")), escape = F)
```
1	  FP   242	    https://github.com/odoo/odoo.git                                                        Completely valid. Miscalculated lifetime
2	  UI   19500	  https://github.com/jordansinger/hook.git                                                JQuery plugin
3	  DOC  147646	https://github.com/coffe1891/frontend-hard-mode-interview.git                           Documentation
4	  BABY 2954146	https://github.com/learnk8s/xlskubectl.git                                              Kubernetes tool, dump or really tiny
5	  UI   160290	https://github.com/arkadiyt/zoom-redirector.git                                         Browser extension
6	  BABY 245099	https://github.com/genderev/prerender.js.git                                            Tool, dump, small?
7	  UI   2560986	https://github.com/alyssaxuu/figma-to-google-slides.git                                 Browser extension, dump
8	  TUT  14642	  https://github.com/feross/md5-password-cracker.js.git                                   Crypto example app
9	  BABY 479104	https://github.com/abeisgoat/-_-.js.git                                                 Joke, UTF emoji replacement for console.warn
10	TUT  16907	  https://github.com/hubwiz/example-node.git                                              Example app
11	UI   2862473	https://github.com/fireship-io/229-multi-level-dropdown.git                             React Widget
12	DEP  140414	https://github.com/zzpiglet/task.git                                                    Not sure, chinese disclaimer, no info, empty main branch, only history
13	UI   3283499	https://github.com/arleyguolei/wx-words-pk.git                                          Some wechat plugin I guess, drop
14	EXT  3027479	https://github.com/anvil-works/anvil-runtime.git                                        Webapp runtime for python, looks like an updated drop
15	BABY 2789884	https://github.com/kikiletgo/universesim.git                                            N body like animation in JS, I guess valid 
16	ERR  1155	  https://github.com/buttplugio/buttplug.git                                              In rust actually - a wifi enabled butt plug sex toy controller IN RUST!!!! I pass no judgement
17	EXT  2489386	https://github.com/lmgonzalves/pieces.git                                               Library to animate images, dump?
18	BABY 297626	https://github.com/danakt/pshe.git                                                      Some git tool, I guess translation to russian? dump
19	EXT  2727169	https://github.com/jeffheaton/encog-javascript.git                                      ML for js, dump   
20	TUT  2965894	https://github.com/nosy-b/holography.git                                                Demo app for tensorflow in browser
21	BABY 2781482	https://github.com/jh3y/meanderer.git                                                   JS library, dump
22	TUT  2768175	https://github.com/gabgoh/epcalc.git                                                    Template app
23	BABY 2784882	https://github.com/johntitus/bungholio.git                                              Tiny twilio bot, real
24	TUT  449919	https://github.com/spite/virtual-webcam.git                                             Proof of concept example 
25	DOC  2841361	https://github.com/cloudflare-internship-2020/internship-application-fullstack.git      Documentation with few lines of js   
26	TUT  2959564	https://github.com/beneater/boids.git                                                   Demonstration
27	BABY 2484702	https://github.com/rauchg/node.dbslayer.js.git                                          Tiny library
28	BABY 3268051	https://github.com/bradtraversy/breaking-bad-cast.git                                   Tiny app to show breaking bad character thigies
29	DOC  12912	  https://github.com/webbushka/atom-react-snippets.git                                    Snippets
30	EXT  2659915	https://github.com/sindresorhus/transliterate.git                                       NPM package, dump?
31	TUT  2737725	https://github.com/fireship-io/223-electron-screen-recorder.git                         Electron tutorial
32	TUT  2749589	https://github.com/wesbos/rona.git                                                      I think tutorial   
33	TUT  562356	https://github.com/gregwolanski/eleventy-tailwindcss-alpinejs-starter.git               Tutorial
34	TUT  2773701	https://github.com/xpoet/node.js-mongodb-movie-site.git                                 Tutorial   
35	TUT  310486	https://github.com/leerob/nextjs-vercel-firebase.git                                    Demo/Dump
36	EXT  3264762	https://github.com/rauchg/jamstack-ecommerce.git                                        Dump
37	BABY 13289	  https://github.com/callahanrts/bar.git                                                  OSX widget, valid   
38	BABY 2482624	https://github.com/jamesgpearce/foxjs.git                                               JS utility
39	BABY 2643119	https://github.com/mathdroid/twitter-dev-salaries-scraper.git                           Simple scrapper
40	BABY 157758	https://github.com/kevinsimler/outbreak.git                                             Disease simulator
41	BABY 139232	https://github.com/coddx-hq/coddx-alpha.git                                             Real tiny thing  
42	BABY 2894249	https://github.com/aruelius/cloud189_greasyfork.git                                     Some chinese could storage client (tiny, but seems legit)
43	TUT  2725730	https://github.com/cornflourblue/react-hooks-redux-registration-login-example.git       React tutorial
44	EXT  408538	https://github.com/jacksoup/hivemetamgr.git                                             Looks like dump, chinese  
45	TUT  3197392	https://github.com/fireship-io/this-video-has-n-views.git                               Youtube API example
46	DOC  728368	https://github.com/pdyck/hearthstone-db.git                                             JSON collection of hearthstone cards, empty to support HongKong protesters  
47	EXT  3012779	https://github.com/broken5/shots.git                                                    Valid, dump
48	TUT  2496533	https://github.com/ddenyss/gulp-template.git                                            Template     
49	BABY 284587	https://github.com/sk7725/commandblocks.git                                             Minecraft mod  
50	DOC  2781687	https://github.com/coding-blocks-archives/data-structures-in-real-life.git              Course Repository   
51	TUT  2496722	https://github.com/natsu90/whoiscomingto.party.git                                      Face recognition ML example   
52	EXT  10070	  https://github.com/credittone/hooker.git                                                Reverse toolkit in chinese, dump

Kind  Java Python JS
FP    0    3      1
EXT   5    7      8
UI    8    0      5
DOC   2    6      5
TUT   2    2      15
BABY  2    8      16
RES   0    5      0
DEP   1    4      1
ERR   0    0      1
Total 20   35     52
